Debiased Calibration for Generalized Two-Phase Sampling

### 2024-12-12 final/paper/paper_ov.tex
Updated final paper.

\begin{abstract}
Generalized entropy calibration \cite{gneiting2007strictly} is a nonparametric
method to estimate survey weights without using the design weights in the
specified loss function. While \cite{kwon2024debiased} explore generalized
entropy calibration to estimate survey weights with known population totals, by
using a two-phase sampling framework, we extend their method to allow for
estimated population totals. We then extend this two-phase sampling framework to
two additional cases: first, when when have two non-nested samples, and
second, when we want to combine three or more samples. 
We apply our method to the Medicare Current Beneficiary Survey for which we
get more efficient estimates by combining ths data set with population level
controls obtained from the Center of Medicare and Medicaid Services as well as
survey data from the U.S. Census' American Community Survey.
\end{abstract}

@@

@@

where  $\bf z_i = (\bf x_i / q_i, g(\pi_{2i|1}^{-1}))$. 
Let $\hat w_{2i|1}$ be the solution to Equation~\eqref{eq:primal}. The resulting 
estimator of $Y_N$ is $\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} \hat w_{2i|1} y_i$.
We can get an estimator using the method of Lagrange multipliers. We need to
minimize the Lagrangian function

@@

  $$
  \hat Y_{\ell}(\bm \lambda, \bm \phi^*) = \hat Y_{DCE}(\hat{\bm \lambda}) + 
  \left(\sum_{i \in A_1} w_{1i} \bf z_i q_i - \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(
  \bm \lambda) z_i q_i\right)\bm \phi^*
  $$

@@

\subsection{Simulation Study 1}

@@

\bibliographystyle{apa}
\bibliography{references}

>>>>

\begin{abstract}
Generalized entropy calibration \cite{gneiting2007strictly} is a nonparametric
method to estimate survey weights without using the design weights in the
specified loss function. While \cite{kwon2024debiased} explore generalized
entropy calibration to estimate survey weights with known population totals, by
using a two-phase sampling framework, we extend their method to allow for
estimated population totals. We then extend this two-phase sampling framework to
two additional cases: first, when we have two non-nested samples, and
second, when we want to combine three or more samples. 
We apply our method to the Medicare Current Beneficiary Survey for which we
get more efficient estimates by combining this data set with population level
controls obtained from the Center of Medicare and Medicaid Services as well as
survey data from the U.S. Census' American Community Survey.
\end{abstract}

@@

\textcolor{red}{The overall structure needs to be changed. You can change the current section 2 to introduce the notation and review the basic properties of the regression estimator in two phase sampling. Section 3 is the main proposal of the debiasing calibration for two-phase sampling. Section 4 is an extension of the proposal to non-nested two-phase sampling and multi-source data integration. The simulation studies in the subsections of Sections 2-4 should be moved to Section 5. The real data analysis in Section 5 should be changed to Section 6. Concluding remarks are made in Section 7. In summary, here is my suggestion for the structure.
\begin{enumerate}
\item Introduction
\item Basic setup: introduce the notation, two-phase regression estimator and its calibration form
\item Main Proposal: introduce debiased calibration for two-phase sampling and discuss its statistical properties 
\item Extensions: \begin{enumerate}
\item Extension to non-nested two-phase sampling 
\item Extension to multi-source data integration
\end{enumerate}
\item Simulation study 
\item Real data analysis 
\item Concluding Remarks 
\end{enumerate}
}

@@

where  $\bf z_i = (\bf x_i / q_i, g(\pi_{2i|1}^{-1}))$. 
\textcolor{red}{Did you use $w_{2i \mid 1}$ to denote $w_{2i}$? Why do you introduce new notation?  } 
Let $\hat w_{2i|1}$ be the solution to Equation~\eqref{eq:primal}. The resulting 
estimator of $Y_N$ is $\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} \hat w_{2i|1} y_i$.
We can get an estimator using the method of Lagrange multipliers. We need to
minimize the Lagrangian function

@@

  %% FIXME: This needs to be defined in terms of \hat Y_{\pi^*}
  $$
  \hat Y_{\ell}(\bm \lambda, \bm \phi^*) = \hat Y_{DCE}(\hat{\bm \lambda}) + 
  \left(\sum_{i \in A_1} w_{1i} \bf z_i q_i - \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(
  \bm \lambda) \bf z_i q_i\right)\bm \phi^*
  $$

@@

\textcolor{red}{This is not enough. We need to discuss variance estimation. }
\subsection{Simulation Study 1}

\textcolor{red}{This subsection should be moved to Section 5. }

@@

\bibliographystyle{apa}
\bibliography{references.bib}
